---
title: "Analysis"
author: "naiadllc"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
    theme: cosmo
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 5,
  dpi = 150
)
```

# Overview

Describe the purpose of this analysis here: the question you're answering,
the data you're using, and the headline findings.

# Setup

```{r libraries}
library(tidyverse)  # dplyr / ggplot2 / readr etc. — used throughout the analysis
library(sf)         # "simple features": reads spatial data as a data frame + geometry
```

# Data

The wetlands live in an ESRI File Geodatabase (`.gdb`). A `.gdb` is really a
*folder* that can hold many layers, so we point `sf` at the folder and name the
specific layer we want.

```{r load-data}
# Forward slashes work on Windows in R and avoid escaping every backslash.
wetlands_gdb <- "D:/Dropbox/Job/Naiad/City of Bozeman/Sensitive Areas Map/GIS Data/Wetlands and WOTUS/Wetlands and WOTUS.gdb"

# This .gdb has 38 layers, so we name the one we want explicitly.
# st_read() returns an "sf" object: a normal data frame with an extra geometry column.
# quiet = TRUE hides the import message so the knitted report stays tidy.
wetlands <- st_read(wetlands_gdb, layer = "MT_NHP_wet_City", quiet = TRUE)

# Sanity check: how many rows (features) and columns did we get?
dim(wetlands)
```

The **attribute table** is just the data without the geometry column — the same
table you'd see in GIS software. `st_drop_geometry()` strips the geometry so the
first few rows print cleanly.

```{r attribute-table}
wetlands |>
  st_drop_geometry() |>
  head()
```

# Exploration

```{r explore}
# Summaries, plots, and sanity checks go here.
```

# Analysis

```{r analysis}
# Core analysis goes here.
```

# Results

Summarize the results and what they mean.

# Session info

```{r session-info}
sessionInfo()
```
